Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes

### 2015-03-20 Answers_for_reviewers.tex

\title{Answers for the Reviewers  for the paper "Proof of uniform convergence for a cell-centered AP discretization of the hyperbolic heat equation on general meshes"}

\author{Emmanuel Franck\footnotemark[1] \footnotemark[2],
C. Buet \footnotemark[3], 
B. Despr\'es\footnotemark[4], 
T. Leroy\footnotemark[4] \footnotemark[3]
}
 \footnotetext[1]{INRIA Nancy Grand-Est and IRMA Strasbourg}
 \footnotetext[3]{CEA, DAM, DIF, F-91297 Arpajon Cedex,France}
 \footnotetext[4]{Laboratoire Jacques-Louis Lions,
  Universit\'e Pierre et Marie Curie,
  75252 Paris Cedex 05,
  France}
\footnotetext[2]{Email adress: emmanuel.franck@inria.fr}

\maketitle

\section{Answers for the report 2M}
\begin{itemize}
\item Constant
\begin{itemize}
\item Page 5 we have modified the constant for the 1D regularity mesh
\item We have correct the constant in the proposition 2.5 page 8
\item 1 : we have corrected the constant in the proposition 2.2 page 7
\item 2 :
\item 3 :
\item 4 :
\item 5 : We have explicit the constant between the equation (32) and the end of the proof of the proposition 2.5
\end{itemize}
\begin{itemize}
\item Comments and suggestions
\begin{itemize}
\item 1: We have added two subsections : "Precisions on AP discretizations" and "Organisation of the proof"
\item 2: we have added 2 sentences about the 2D Riemann problem and the nodal scheme. 
\item 3: We have added a sentence to explain why we use this formulation of the scheme and not the classical Gosse-Toscani scheme. For the remark about " the authors choose to renounce to the well- balanced property of the original 1D Gosse-Toscani scheme (except on uniform Cartesian grids) while retaining only its AP character" it is not clear that we say that. Indeed the scheme is well balanced for a subset of steady states (see annex of the paper "design of AP scheme ..."): the steady state associated to $u=Cts$ and $p$ linear. This property is perhaps impotent for the uniform convergence. At the end we renounce only to the steady states associated to $\nabla{u}=\nabla\times \phi$ with $\phi$ a potential. 
\item 4: We have correct this part introducing $v$ to obtain a not confusing proof.
\item 5: We have replaced is $\mathbf{u}^{\eps}$ by $u^{\eps}$
\item 6 : We have replaced the proposition 2.8 by the Lemma 2.8
\item 7 : We have added the reference on the paper "Time asymptotic high order ..." at the end of the 2D in the numerical results.
\item 8 : We have corrected the proposition 
\item 9 : We have added the missing "("
\end{itemize}
\item Minor issues and Typos
\begin{itemize}
\item 1: We have replaced $P^0$ by "first order"
\item 2 : we have corrected this sentence 
\item 3 : we have corrected this sentence 
\item 4 : we have corrected this sentence. (17) correspond to the scheme not the smooth data.
\item 5 : we have corrected this sentence. 
\item 6 : we have corrected your two remarks in this page 
\item 7 : we have corrected this sentence. 
\item 8: We have replaced $\gamma$ by $\tau$ in the numeric part.
\item 9: The date for the L. Gosse paper have been modified. for the S. Jin article we have copy the reference written on the website of S. Jin 
\end{itemize}
\end{itemize}
\end{document}

### 2015-03-20 Corrected_version.tex
correction thomas

The natural cellwise initialization is chosen
\begin{equation} \label{eq:initp1}
p_j^\eps(0)=p_0(x_j) \mbox{ and }
u_j^\eps(0)=-\frac\eps\sigma \partial_x p_0(x_j) \mbox{ for all }j\in \mathbb Z.
\end{equation}
Our goal is this section is to show that this scheme is AP.

When $\eps$ tends to $0$, 
 the scheme $P_h^\eps$ admits the 
diffusion limit scheme $P_h^0$
\begin{equation}\label{schemadifff}
P_h^0: \qquad
\displaystyle\Delta x_j\frac{d}{dt} p_j -\frac{1}{\sigma } \bigg(
\frac{p_{j+1}-p_j}{\Delta x_{j+\frac12 }}-\frac{p_j -p_{j-1}}{\Delta
x_{j-\frac12 }}\bigg)=0
\end{equation}

@@

\begin{proposition} \label{heqtode}
There exists a constant $C>0$ such that 
\begin{equation*}
\|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
C \eps  \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
\end{equation*}
\end{proposition}
\begin{proof}
We define $v=-\frac{\varepsilon}\sigma \partial_x p$ with $p$ the diffusion solution of (\ref{difffff}) and
introduce $R^{\eps}$ such that the solution of the diffusion equation satisfies
\begin{equation}\label{modifdiff}
\left \{
\begin{array}{lll}
\dt p +\frac{1}{\eps}\partial_{x}v=0,\\
\partial_t v+ \frac{1}{\eps}\partial_x p +\frac{\sigma}{\eps^2}v = R^{\eps}
\end{array}
\right.
\end{equation}
where
 $R^{\eps}=\dt v=-\frac{\varepsilon}\sigma \partial_{tx} p=
-\frac{\varepsilon}{\sigma^2} \partial_{xxx}p$. 
Note that 
$\|R^{\eps}(t)\|_{L^2(\mathbb{R})}\leq \|R^{\eps}(0)\|_{L^2(\mathbb{R})}$. 
Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=v-u^{\eps}$, we make the difference between the
systems \eqref{chaleur22} et \eqref{modifdiff}
\begin{equation}\label{diffmodif}
\left \{
\begin{array}{lll}
\dt e^{\eps} +\frac{1}{\eps}\partial_{x}f^{\eps}=0,\\
\partial_t f^{\eps} +\frac{1}{\eps}\partial_x e^{\eps} +\frac{\sigma}{\eps^2}f^{\eps} = R^{\eps}.
\end{array}
\right.
\end{equation}
Since data are well-prepared, one has $e^{\eps}(0)=f^{\eps}(0)=0$.
Consider
$\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2=\|e^{\eps}\|_{L^2(\mathbb{R})}
^2+\|f^{\eps}\|_{L^2(\mathbb{R})}^2$.
Adding the first equation of
\eqref{diffmodif} multiplied by $e^{\eps}$ and the second multiplied by $f^{\eps}$ and integrating
on $\mathbb{R}$,
 we find out that:
$\frac12 \frac{d}{dt}\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2 \leq
\int_{\mathbb{R}}R^{\eps}f^{\eps} dx \leq  \|R^{\eps}\|_{L^2(\mathbb{R})}
\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}
.$
  The proof is ended by integration between 0 and T.

@@

\begin{proof}
According to the above remark we obtain  
the formulation 
(\ref{schema}) 
which is 
equivalent to $P_h^\eps$
\begin{equation}\label{schema}
\left\{
\begin{array}{lll}
\displaystyle\Delta x_j\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
u_{j-\frac12 }^{\eps} }{\eps} = 0,\\
\displaystyle\Delta x_j\frac{d}{dt}u^{\eps}_j-\frac{u_{j+\frac12 }^{\eps}+
u_{j-\frac12 }^{\eps}}{\eps} +\frac{2}{\eps}u_j^{\eps}=0, \\
\displaystyle 
\left( 2
+\frac{\sigma \Delta x_{j+\frac12}
 }{\eps}
\right) u_{j+\frac12 }^{\eps}

=p^{\eps}_j-p^{\eps}_{j+1}+u^{\eps}_j+u^{\eps}_{j+1}
.
\end{array}
\right.
\end{equation}
Consider now the discrete quadratic energy
$E(t)=\frac12 \sum_j \Delta x_j ((p^{\eps}_j)^2+(u^{\eps}_j)^2)$.
 Multiplying the first equation of \eqref{schema} by $p_j^{\eps}$ and the second
equation by $u_j^{\eps}$ and adding on all the cells, one finds
\begin{equation*}
 E'(t)=-\sum_{j\in \mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps}}{\eps}p^{\eps}_j + \sum_{j\in
\mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{\eps}u^{\eps}_j
-\frac{2}{\eps}\sum_j (u^{\eps}_j)^2.
\end{equation*}
Since $
\sum_{j}(
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps})p^{\eps}_j =
\sum_{j} u_{j+\frac12 }^{\eps}(p^{\eps}_j-p^{\eps}_{j+1})$, one
has  by using the third equation of \eqref{schema} and rearranging the
terms
\begin{equation}\label{prodentrgosseeq}
E'(t)+\sum_{j\in \mathbb{Z}} \frac{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps}+\sum_{j\in \mathbb{Z}} \frac{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps} +
\frac{\sigma}{\eps^2}\sum_{j\in \mathbb{Z}} \Delta x_{j}
\frac{(u_{j+\frac12 }^{\eps})^2+(u_{j-\frac12 }^{\eps})^2}{2}= 0.
\end{equation}
Integrating  \eqref{prodentrgosseeq} between 0 and t, one finds  $E(t)\leq E(0)$, that is the $L^2$ stability of $P_h^\eps$.
The estimate  (\ref{estiuepsflux}) 
comes from 
$\Delta x_{j+\frac12}=\frac12( \Delta x_{j}+\Delta x_{j+1})$. The estimate 
 (\ref{estiuepsflux2}) is directly deduced from
(\ref{prodentrgosseeq}).
\end{proof}

@@

In this section we  
prove the 
convergence of $P_h^\varepsilon $ to  $P^\varepsilon $. We still denote $V^\eps(t)=(p^\eps,u^\eps)$.
\begin{proposition}\label{cv1d}
There exist a constant $C(T)>0$ independent of $\eps$ and $h$ 
 such that the following estimate holds 
\begin{equation*}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq C(T) 
\sqrt \frac{h}\eps 
\left\| \V^{\eps}(0)
\right\|_{H^1(\mathbb{R})}.
\end{equation*}

@@

\|  u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }.

Since $\| u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
$
\frac{\sigma}
{\eps^2}\| u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) }\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1} ) and (\ref{bee2} ), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and estimate \eqref{estiuepsflux}, one can find a constant $C\geq0$ such that the next term can be  bounded like 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq C h \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \| u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent so 
 $\mathscr{E}(0)\leq Ch^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq C(T) \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We  first 
 recall a fundamental   error estimate \cite{FV}
for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data.
. 
\begin{proposition}\label{ds1d}
There exists a constant $C(T)>0$ such that
\begin{equation*}
\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
C(T)h \| \partial_{xxx}p_0 \|_{L^2(\mathbb{R})  }.
\end{equation*}
\end{proposition}

@@

\sigma^{-1}\| s_h\|_{L^2(\mathbb{R})} \|e_h\|_{L^2(\mathbb{R})}+
\frac12 \|r_h\|^2_{L^2(\mathbb{R})}.
Using the  definitions of  the truncation errors $s_h$ and $r_h$, these
quantites can be   
bounded independently of the time of observation $T$ 

@@

\left\| 
\frac{e_{j+1}-e_{j}}{\Delta x_{j+\frac12 }} \right\|_{
\leq C(T) h 
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}

@@

\left\| 
\frac{p_{j+1}-p_{j}}{\Delta x_{j+\frac12 }} -\partial_x p (x_{j+\frac12}) \right\|_{
\leq C(T) h 
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
\right).

@@

}\leq C(T) h \eps \left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})}
\right).
Finally, 

>>>>

The natural cellwise initialization is chosen
\begin{equation} \label{eq:initp1}
p_j^\eps(0)=p_0(x_j) \mbox{ and }
u_j^\eps(0)=-\frac\eps\sigma \partial_x p_0(x_j) \mbox{ for all }j\in \mathbb Z.
\end{equation}
Our goal is this section is to show that this scheme is AP. When $\eps$ tends to $0$, 
 the scheme $P_h^\eps$ admits the 
diffusion limit scheme $P_h^0$
\begin{equation}\label{schemadifff}
P_h^0: \qquad
\displaystyle\Delta x_j\frac{d}{dt} p_j -\frac{1}{\sigma } \bigg(
\frac{p_{j+1}-p_j}{\Delta x_{j+\frac12 }}-\frac{p_j -p_{j-1}}{\Delta
x_{j-\frac12 }}\bigg)=0
\end{equation}

@@

\begin{proposition} \label{heqtode}
There exists a constant which depend of the time such that 
\begin{equation*}
\|\V^{\eps}-\W^\eps\|_{L^\infty([0,T];L^2(\mathbb{R}) )} \leq
 \eps \frac{T}{\sigma^2} \|\partial_{xxx}p_0\|_{L^2(\mathbb{R})}.
\end{equation*}
\end{proposition}
\begin{proof}
We define $v=-\frac{\varepsilon}\sigma \partial_x p$ with $p$ the diffusion solution of (\ref{difffff}) and
introduce $R^{\eps}$ such that the solution of the diffusion equation satisfies
\begin{equation}\label{modifdiff}
\left \{
\begin{array}{lll}
\dt p +\frac{1}{\eps}\partial_{x}v=0,\\
\partial_t v+ \frac{1}{\eps}\partial_x p +\frac{\sigma}{\eps^2}v = R^{\eps}
\end{array}
\right.
\end{equation}
where
 $R^{\eps}=\dt v=-\frac{\varepsilon}\sigma \partial_{tx} p=
-\frac{\varepsilon}{\sigma^2} \partial_{xxx}p$. 
Note that 
$\|R^{\eps}(t)\|_{L^2(\mathbb{R})}\leq \|R^{\eps}(0)\|_{L^2(\mathbb{R})}$. 
Denoting $e^{\eps}=p-p^{\eps}$, $f^{\eps}=v-u^{\eps}$, we make the difference between the
systems \eqref{chaleur22} et \eqref{modifdiff}
\begin{equation}\label{diffmodif}
\left \{
\begin{array}{lll}
\dt e^{\eps} +\frac{1}{\eps}\partial_{x}f^{\eps}=0,\\
\partial_t f^{\eps} +\frac{1}{\eps}\partial_x e^{\eps} +\frac{\sigma}{\eps^2}f^{\eps} = R^{\eps}.
\end{array}
\right.
\end{equation}
Since data are well-prepared, one has $e^{\eps}(0)=f^{\eps}(0)=0$.
Consider
$\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2=\|e^{\eps}\|_{L^2(\mathbb{R})}
^2+\|f^{\eps}\|_{L^2(\mathbb{R})}^2$.
Adding the first equation of
\eqref{diffmodif} multiplied by $e^{\eps}$ and the second multiplied by $f^{\eps}$ and integrating
on $\mathbb{R}$,
 we find out that:
$\frac12 \frac{d}{dt}\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}^2 \leq
\int_{\mathbb{R}}R^{\eps}f^{\eps} dx \leq  \|R^{\eps}\|_{L^2(\mathbb{R})}
\|\V^{\eps}-\W^\eps\|_{L^2(\mathbb{R})}
.$
  The proof is ended by integration between 0 and T.

@@

\begin{proof}
According to the above remark we obtain  
the formulation 
(\ref{schema}) 
which is 
equivalent to $P_h^\eps$
\begin{equation}\label{schema}
\left\{
\begin{aligned}
&\Delta x_j\frac{d}{dt}p^{\eps}_j +\frac{u_{j+\frac12 }^{\eps} -
u_{j-\frac12 }^{\eps} }{\eps} = 0,\\
&\Delta x_j\frac{d}{dt}u^{\eps}_j-\frac{u_{j+\frac12 }^{\eps}+
u_{j-\frac12 }^{\eps}}{\eps} +\frac{2}{\eps}u_j^{\eps}=0, \\
&
\left( 2
+\frac{\sigma \Delta x_{j+\frac12}
 }{\eps}
\right) u_{j+\frac12 }^{\eps}

=p^{\eps}_j-p^{\eps}_{j+1}+u^{\eps}_j+u^{\eps}_{j+1}
.
\end{aligned}
\right.
\end{equation}
Consider now the discrete quadratic energy
$E(t)=\frac12 \sum_j \Delta x_j ((p^{\eps}_j)^2+(u^{\eps}_j)^2)$.
 Multiplying the first equation of \eqref{schema} by $p_j^{\eps}$ and the second
equation by $u_j^{\eps}$ and adding on all the cells, one finds
\begin{equation*}
 E'(t)=-\sum_{j\in \mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps}}{\eps}p^{\eps}_j + \sum_{j\in
\mathbb{Z}} \frac{
u_{j+\frac12 }^{\eps}+u_{j-\frac12 }^{\eps}}{\eps}u^{\eps}_j
-\frac{2}{\eps}\sum_j (u^{\eps}_j)^2.
\end{equation*}
Since $
\sum_{j}(
u_{j+\frac12 }^{\eps}-u_{j-\frac12 }^{\eps})p^{\eps}_j =
\sum_{j} u_{j+\frac12 }^{\eps}(p^{\eps}_j-p^{\eps}_{j+1})$, one
has  by using the third equation of \eqref{schema} and rearranging the
terms
\begin{equation}\label{prodentrgosseeq}
E'(t)+\sum_{j\in \mathbb{Z}} \frac{
(u_{j+\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps}+\sum_{j\in \mathbb{Z}} \frac{
(u_{j-\frac12 }^{\eps}-u^{\eps}_j)^2 }{\eps} +
\frac{\sigma}{\eps^2}\sum_{j\in \mathbb{Z}} \Delta x_{j}
\frac{(u_{j+\frac12 }^{\eps})^2+(u_{j-\frac12 }^{\eps})^2}{2}= 0.
\end{equation}
Integrating  \eqref{prodentrgosseeq} between 0 and t, one finds  $E(t)\leq E(0)$, that is the $L^2$ stability of $P_h^\eps$.
The estimate  (\ref{estiuepsflux}) 
comes from 
$\Delta x_{j+\frac12}=\frac12( \Delta x_{j}+\Delta x_{j+1})$. The estimate 
 (\ref{estiuepsflux2}) is directly deduced from
(\ref{prodentrgosseeq}).
\end{proof}

@@

In this section we  
prove the 
convergence of $P_h^\varepsilon $ to  $P^\varepsilon $. We still denote $V^\eps(t)=(p^\eps,u^\eps)$.
\begin{proposition}\label{cv1d}
Under assumption \ref{geometrie1d} on the mesh and assuming that the initial conditions satisfy \eqref{eq:initp1}, the following estimate holds

\begin{equation*}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} }
\sqrt \frac{h}\eps 
\left\| \V^{\eps}(0)
\right\|_{H^1(\mathbb{R})}.
\end{equation*}

@@

\|  u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R)) }.

Since $\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq t \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$ and also 
\frac{\sigma}
{\eps^2}\| \mathbf u^\eps  \|^2_{ L^2( [0,t] : H^1(\mathbb R) )}\leq  \| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$
by (\ref{bee1}) and (\ref{bee2}), one gets that
\begin{equation} \label{eq:sm1}
\left( \frac{1}{\eps}+\frac{\sigma}{2\eps^2}\right)
\int_0^t 
\sum_{j\in \mathbb{Z}} 
\left ( 
\delta_{j}^+(u^{\eps})^2+\delta_{j}^-(u^{\eps})^2\right )dt
\leq  h  \left( \frac{t}\eps+\frac{1}{2}\right)
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
A similar and simpler formula for the next terms is
\begin{equation} \label{eq:sm2}
 \frac{1}{\eps}\int_0^t 
 \sum_{j\in \mathbb{Z}} 
 \left (
\delta_{j}^+(p^{\eps})^2+\delta_{j}^-(p^{\eps}
)^2\right ) \leq   \frac{ h t}\eps 
\|  p^\eps  \|^2_{  H^1(\mathbb R) }
\leq     \frac{ h t}\eps 
\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{equation}
Next, using the assumption \eqref{geometrie1d} on the mesh and the estimate \eqref{estiuepsflux}, one controls the next term by 
\begin{equation} \label{eq:sm3}
 \int_0^T \underset{j\in \mathbb{Z}}{\sum} \frac{1}{8\eps} \sigma \Delta x_j^2
\frac{(u_{j-\frac12 }^{\eps})^2+(
u_{j+\frac12 }^{\eps})^2}{\eps} \leq  \frac{h}{4C_{\mathcal{M}}} \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2.
\end{equation}
Finally the last term in (\ref{eq:eqn1}) can be bounded using a
Cauchy-Schwarz inequality 
$$
\frac{\sigma^2}{4\eps^3} \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \|  u^\eps  \|^2_{  L^2(\mathbb R) }
$$
so that
\begin{equation} \label{eq:sm4}
\frac{\sigma^2}{4\eps^3} 
\int_0^t 
 \sum_{j\in
\mathbb{Z}}\bigg( {\int_{x_{j-\frac12}}^{x_{j+\frac12}}} u^{\eps}(x) dx \bigg)^2
\leq 
\frac{\sigma^2}{4\eps^3}
h \| u^\eps  \|^2_{  L^2([0,t]\times \mathbb R) }
\leq 
\frac{\sigma}{4\eps}
h  \|\mathbf{V}^{\eps}(0)\|_{L^2(\mathbb{R})}^2
\end{equation}
by means of the energy identity.
 So using (\ref{eq:sm1}-\ref{eq:sm4}) we obtain for all time $t\leq T$:
\begin{eqnarray*}
\mathscr{E}(t) \leq
\mathscr{E}(0)+h
\left( \frac{t}{\eps}+\frac{1}2 + \frac{t}{\eps}+C+\frac{\sigma
}{4\eps}\right)\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2.
\end{eqnarray*}
The initialization stage is consistent (equation \ref{eq:initp1}) so 
 $\mathscr{E}(0)\leq h^2\| \V^{\eps}(0) \|_{H^1(\mathbb{R})}^2$.
 Making use of the  initial remark \ref{sigmanotzero}, one   obtains 
\begin{equation*}\label{esti1}
\|\V^{\eps}-\V^{\eps}_h \|_{L^2([0,T]\times \mathbb{R})}
\leq \sqrt{h\eps + 2t + \frac{\eps}{2} + \frac{\eps}{4C_{\mathcal{M}}} + \frac{\sigma}{4} } \sqrt{ \frac{h}{\eps}}
\| \V^{\eps}( 0)
\|_{H^1(\mathbb{R})}, \qquad C(T)\geq0.
\end{equation*}
The proof is ended.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We  first 
 recall a fundamental   error estimate \cite{FV}
for the diffusion limit scheme \eqref{schemadifff}, assuming smooth initial data \eqref{eq:intip0}. 
\begin{proposition}\label{ds1d}
There exists a constant $C(T)>0$ such that
\begin{equation*}
\|\W_h^\eps-\W^\eps\|_{L^{\infty}([0,T];L^2(\mathbb{R}))} \leq
C(T)h \| \partial_{xxx}p_0 \|_{L^2(\mathbb{R})  }.
\end{equation*}
\end{proposition}

@@

\frac{1}{\sigma}\| s_h\|_{L^2(\mathbb{R})} \|e_h\|_{L^2(\mathbb{R})}+
\frac{1}{2\sigma} \|r_h\|^2_{L^2(\mathbb{R})}.
Using the  definitions of  the truncation error $s_h$, one easily obtains by using classical arguments $\|s_h\|_{L^2([0,T]\times\mathbb{R})}\leq \sqrt{2}h\|\partial_{xxx}p\|_{L^2([0,T]\times\mathbb{R})}$. Since $p$ satisfies the diffusion equation \eqref{difffff}, one gets $\|\partial_{xxx}p\|_{L^2([0,T]\times\mathbb{R})} \leq \sqrt{\sigma/2} \|\partial_{xx}p_0\|_{L^2(\mathbb{R})}$. The same manipulations on the second truncation error $r_h$ yields

@@

\int_0^T \sum_j
\frac{(e_{j+1}-e_{j})^2}{\Delta x_{j+\frac12 }}\leq h^2
\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}^2 +
 \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}^2 
\right)\bigg( \sigma + Te^{T/\sigma} \bigg) ,

@@

\int_0^T \sum_j \Delta x_{j+\frac12 } \bigg|
\frac{p_{j+1}-p_{j}}{\Delta x_{j+\frac12 }} -\partial_x p (x_{j+\frac12})  \bigg|^2
\leq 2 h^2
\left(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}^2 +
 \|\partial_{x}p_0   \| _{L^2(\mathbb{R})}^2 
\right)\bigg( 3 \sigma + Te^{T/\sigma} \bigg).

@@

}\leq  h \eps \bigg(  \|\partial_{xx}p_0   \| _{L^2(\mathbb{R})}+
 \|\partial_{xxx}p_0   \| _{L^2(\mathbb{R})} \bigg) \sqrt{\frac12 + \frac{4}{\mathcal{C}_M}\bigg( 3 + \frac{T}{\sigma}e^{T/\sigma} \bigg) }
,
where the constant $\mathcal{C}_M$ is defined in assumption \ref{geometrie1d}. Finally, 
